factor_explorer

### 2014-06-21 ijlyttle/factor_explorer.Rmd
gets student explorer going

# using pv1 for now
var_names_student_subject <- c(
  math = "PV1MATH",
  science = "PV1SCIE",
  reading = "PV1READ"
)

@@

tmp <- var_names_student_factor[var_names_student_factor == var_names_student] 
```

@@

selectInput(
  "country",
  label = "Countries",
  choices = levels(student2012$CNT),
  selected = "Albania",
  multiple = TRUE
)

# selectInput(
#   "factor"
#   label = "Factor",
#   choices = 
# )
```

```{r shiny_transform, echo = FALSE}
rct_data <- reactive({
  df <- 
    student2012 %>%
    filter(CNT %in% input$country)

})

renderPlot({
  ggplot(
    data = rct_data()
  ) + 
  geom_violin(
    aes_string(x = "factor(ST06Q01)", 
               y = input$subject), 
    scale = "width"
  )
})

```

>>>>

var_names_student_subject <- 
  var_names_student[c(
    seq(501, 505), # math
    seq(541, 545), # reading
    seq(546, 551)  # science
  )]

@@

var_names_factor <- var_names_student[var_names_student %in% var_names_student_factor] 
```

@@

selectInput(
  "country",
  label = "Countries",
  choices = levels(student2012$CNT),
  selected = c("United States of America", "Canada"),
  multiple = TRUE
)

selectInput(
  "x_factor",
  label = "X-axis factor",
  choices = var_names_factor,
  selected = "ST04Q01"
)

selectInput(
  "fill_factor",
  label = "Fill factor",
  choices = var_names_factor,
  selected = "ST26Q03"
)
```

```{r shiny_transform, echo = FALSE}
rct_data <- reactive({
  df <- 
    student2012 %>%
    filter(CNT %in% input$country) 
})

val_get_name <- function(x, lst){
  names(lst[lst == x])[[1]]
}

rct_count <- reactive({
  df <-
    rct_data() %>%
    group_by()
})

rct_labels <- reactive({
  list(
    x = input$x_factor %>% val_get_name(var_names_factor),
    y = input$subject %>% val_get_name(var_names_student_subject),
    fill = input$fill_factor %>% val_get_name(var_names_factor)
  )
})

renderPlot({
  ggplot(
    data = rct_data()
  ) + 
  geom_violin(
    aes_string(
      x = input$x_factor, 
      y = input$subject),
      scale = "width"
  ) + 
  geom_boxplot(
    aes_string(
      x = input$x_factor,
      y = input$subject,
      fill = input$fill_factor
    )  
  ) + 
  facet_grid(CNT ~ .) + 
  scale_x_discrete(name = rct_labels()[["x"]]) +  
  scale_y_continuous(limits = c(0, 1000), name = rct_labels()[["y"]]) +
  scale_fill_discrete(name = rct_labels()[["fill"]]) 
})
```
